---
title       : Dose-Response Estimation for Radiation
subtitle    : Survival time of rats exposed to radiation
author      : Edward D. Browne
job         : Researcher
logo        : slidify_logo.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]           # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

###logo        : clipart.jpeg
###logo        : clipart.pdf


--- &twocol

## Motivation

*** =left

We have an experimental dataset of the measured survival 
time for rats exposed to radiation for a small set of values of radiation.
A model to predict the survival time for exposure to any arbitrary dose
of radiation would be extremely valuable.
<p>
Through detailed analysis of the dataset, we arrived at the optimal
linear model to represent cause-and-effect relationship inherent in
the survival time resulting from the given dose of radiation administered
to the subject rats
</p>

*** =right

```{r, echo=5}
library(boot)
library(polynom)
#From R's 'boot' dataset, "survival" is length of Survival of Rats after Radiation Doses
plot(survival, main = "Fig. 1 - Plot of raw 'survival' dataset",
     xlab = "radiation exposure (in RAD)",
     ylab = "Survival (in units of time)")
```

---

## The result of our analysis is a quadratic curve

$y = 49.667 - 0.112x + 0.0000566x^2$

Using this predictive function, we will be able to predict the survival time
for any arbitrary dose of radiation with a 95% confidence level

---

## 

<div class="red2">

<b> This newfound ability to predict survival for untested doses gives us many benefits:</b>

</div>

<p> </p>



> - Reduces need for laboratory rats
> - Reduces unnecessary exposure for research personnel to radiation
> - Saves time and money


--- &twocol

## Summary of Analytic Results

*** =left
Raw data, from Rat Radiation Experiment

```{r, echo=FALSE}
library(boot)
library(polynom)
#From R's 'boot' dataset, "survival" is length of Survival of Rats after Radiation Doses
plot(survival, main = "Fig. 2 - Plot of raw 'survival' dataset",
     xlab = "radiation exposure (in RAD)",
     ylab = "Survival (in units of time)")
```

*** =right
Linear model, quadratic degree, fitted to data
```{r, echo=FALSE}
x <- survival$dose
y <- survival$surv
# lm fits a linear model to the data to the desired degree (quadratic, in this case)
ret <- lm( formula = y ~ x + I(x^2))
#the 'ret' object contains a named vector called 'coefficients', 
coeff <- unname(ret$coefficients)
# coeff now contains only the coefficients without names, in ascending order of power
# The polynomial function constructs a polynomial object from a vector of coefficients
mypoly <- polynomial(coeff)
plot(mypoly)

```
*** =fullwidth
---




